Lens Recovery with GLASS: An Extensible Free-Form Gravitational Lens Modeling Framework

### 2013-05-27 limits/ms.tex
Added back main results plot. Extended the vel. disp. plot to a larger radius.

The galaxies were
first generated as three dimensional particle distributions with the
tool DEHNEN-TOOL. Each component follows the profile
\begin{equation}
\rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}}
\label{Dehnen profile}
\end{equation}
where $\gamma$ is the profile index and $a$ is the scale radius.  In the
case $\gamma=1$ this is the Hernquist profile.  The four combinations of
profile indices are shown in \tabref{Lens profile params}.  Note that two of
the galaxies have $\gamma_\mathrm{DM}=1$. While we know from simulations that a
more accurate approximation would be an NFW or Einasto profile we are not
probing the outer regions of the halo where the difference would be most
extreme.  The Hernquist profile is easier to generate as it has finite mass.

\begin{table}
\begin{tabular}{cllllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & $\Rmap$ & Notes\\
\hline
AA & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc & \\
AC & 1 & 4 & 1 & $11^2$ & 50 kpc & \\
BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc & \\
BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc & 
\end{tabular}
\caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $1.8\e{10}\Msun$. The scale lengths for
all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
\label{Lens profile params}
\end{table}

@@

The main results from modeling these different configuration are shown black in
\figref{Test reconstructions}. Each subplot corresponds to a different galaxy and
the vertical axis shows the range of quality.  The quality of a
model $\M_i$ by comparing the recovered density profile $\rho_\M(r)$ against
the profile of the mock galaxy $\rho_G(r)$.  In particular, the plots show the
RMS quantity
%
\begin{equation}
  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
\end{equation}
%
\begin{figure}
%\plotone{AAarrival_surfaces}
%\plotone{BBarrival_surfaces}
\plotone{BCarrival_surfaces}
\caption{The lens configurations for the six test cases using the BC mock galaxy. Here,
the central image is shown, although not all tests include it. The central image belongs
to only one set of images to avoid overconstraining the models. Similar colors group
images that share a common source. In the case of the extended image systems the source
is at the same redshift, while the redshift is varied between the systems in the 
ZConstrast cases. Grey circles are a visual aid to help determine radial separation
between images. The axes are measure in arcseconds.}
\label{Test reconstructions}
\end{figure}

@@

%\section{Results} %--------------------------------------------------------------

%\begin{figure}
%\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
%\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
%\end{figure}

>>>>

The galaxies were
first generated as three dimensional particle distributions with the
tool DEHNEN-TOOL. Each component follows the profile
\begin{equation}
\rho(r) = \frac{M}{4\pi a^3}(3-\gamma){(r/a)^{-\gamma}(1 + r/a)^{\gamma-4}}
\label{Dehnen profile}
\end{equation}
where $\gamma$ is the profile index and $a$ is the scale radius.  In the
case $\gamma=1$ this is the Hernquist profile.  The four combinations of
profile indices are shown in \tabref{mock galaxy params}.  Note that two of
the galaxies have $\gamma_\mathrm{DM}=1$. While we know from simulations that a
more accurate approximation would be an NFW or Einasto profile we are not
probing the outer regions of the halo where the difference would be most
extreme.  The Hernquist profile is easier to generate as it has finite mass.

\begin{table}
\begin{tabular}{cllllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & $\Rmap$ & Notes\\
\hline
AA & 1 & 4 & 0.05 & $11^{2.95}$ & 50 kpc & \\
AC & 1 & 4 & 1 & $11^2$ & 50 kpc & \\
BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & 50 kpc & \\
BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 10 kpc & 
\end{tabular}
\caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $1.8\e{10}\Msun$. The scale lengths for
all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
\label{mock galaxy params}
\end{table}

@@

The main results from modeling these different configuration are shown black in
\figref{main results}. Each subplot corresponds to a different galaxy and
the vertical axis shows the range of quality.  The quality of a
model $\M_i$ by comparing the recovered density profile $\rho_\M(r)$ against
the profile of the mock galaxy $\rho_G(r)$.  In particular, the plots show the
RMS quantity
%
\begin{equation}
  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
\end{equation}
%

\begin{figure}
\plottwo{AAchi2_profile.pdf}{BBchi2_profile.pdf}
\plottwo{ACchi2_profile.pdf}{BCchi2_profile.pdf}
\caption{The main results showing the quality of model recovery. Each panel corresponds to 
the named mock galaxy, whose parameters are listed in \tabref{mock galaxy params}. Within
each panel are six groups of results for each of six lens morphologies. Each morphology
considered the presence of time delays and a central image. The black markers are for tests
that did not include the stellar mass as a lower bound constraint, while the red markers
indicate where the stellar mass has been given.}
\label{main results}
\end{figure}

\begin{figure}
%\plotone{AAarrival_surfaces}
%\plotone{BBarrival_surfaces}
\plotone{BCarrival_surfaces}
\caption{The lens configurations for the six test cases using the BC mock galaxy. Here,
the central image is shown, although not all tests include it. The central image belongs
to only one set of images to avoid overconstraining the models. Similar colors group
images that share a common source. In the case of the extended image systems the source
is at the same redshift, while the redshift is varied between the systems in the 
ZConstrast cases. Grey circles are a visual aid to help determine radial separation
between images. The axes are measure in arcseconds.}
\label{reconstruction}
\end{figure}

@@

\section{Results} %--------------------------------------------------------------
